---
title: "Homework13"
author: "Larine Hamied"
date: "12/10/2018"
output: html_document
---
#Homework 13 
```{r}
library(dplyr)
library(magrittr)
library(caret)
library(nnet)
```

```{r}
show_number <- function(m, i, oriented=T)
{
  im <- matrix(mtrain[i,], byrow=T, nrow=28)
  
  if (oriented) {
    im_orient <- matrix(0, nrow=28, ncol=28)
    for (i in 1:28)
      im_orient[i,] <- rev(im[,i])
    
    im <- im_orient
  }
  image(im)
}
```

Calling in the training datasets, parsing it and changing the sample labels so that each sample is labeled as 0 if the image is not a 3 and 1 if the image is a 3.
```{r}
if (!exists("mtrain")) {
  mtrain <- read.csv("mnist_train.csv", header=F) %>% as.matrix
  for (i in 1:nrow(mtrain)){
    cn <- mtrain[i,1]
    if (cn == "3"){
      mtrain[i,1] <- 1
    } 
    else {mtrain[i,1] <- 0}
  }
  train_classification <- mtrain[,1]
  mtrain <- mtrain[,-1]/256
  colnames(mtrain) <- 1:(28*28)
  rownames(mtrain) <- NULL
}
```

Looking at a sample: 
```{r}
show_number(mtrain, 8)
```

Filtering to use the first 1000 mnist samples: 
```{r}
x <- mtrain[1:1000,]
colnames(x) <- 1:784
y <- factor(train_classification[1:1000])
```

Prediction error function to get an idea of how different the test data is than the training data later: 
```{r}
prediction_errors <- function(data, nnet)
{
  true_y <- y
  pred_y <- predict(nnet, x)
  
  n_samples <- nrow(x)
  error <- sum(true_y != pred_y)/n_samples
  return (error)
}
```

##Training neural net to identify images of the number 3.
###Part I) Using the parameter decay = 0 
```{r}
tuning_df <- data.frame(size=8:12, decay=0)

fitControl <- trainControl(method="none")

fitControl <- trainControl(## 2-fold CV
  method = "repeatedcv",
  number = 2,
  ## repeated ten times
  repeats = 3)

t_out <- caret::train(x=x, y=y, method="nnet",
                      trControl = fitControl,
                      tuneGrid=tuning_df, maxit=100000, MaxNWts = 10000)
```


###Part II) Assign a parameter for decay based on cross validation 
```{r}
tuning_df <- data.frame(size=8:12, decay=c(0, .1, .5, 1, 2))

fitControl <- trainControl(method="none")

fitControl <- trainControl(## 2-fold CV
  method = "repeatedcv",
  number = 2,
  ## repeated ten times
  repeats = 3)

t_out2 <- caret::train(x=x, y=y, method="nnet",
                      trControl = fitControl,
                      tuneGrid=tuning_df, maxit=100000, MaxNWts = 10000)
```

##Testing the test dataset to evaluate the accuracy of the neural net 
```{r}
if (!exists("mtest")) {
  mtest <- read.csv("mnist_test.csv", header=F) %>% as.matrix
  for (i in 1:6000){
    cn <- mtest[i,1]
    if (cn == "3"){
      mtest[i,1] <- 1
    } else {
      mtest[i,1] <- 0
    }
  }
  test_classification <- mtest[,1]
  mtest <- mtest[,-1]/256 
  colnames(mtest) <- 1:(28*28)
  rownames(mtest) <- NULL
}
x2 <- mtest[1:1000,]
colnames(x2) <- 1:784
y2 <- factor(train_classification[1:1000])
```

```{r}
prediction_errors(mtest,t_out)
prediction_errors(mtest,t_out2)
```

